Calculate minhash pairs manually

### 2015-10-08 008-pairwise-jaccard.Rmd
Round matrix
Simplify notebook generation, improve figures

---
title: "Compare pairwise with Jaccard similarity"
author: "Lincoln Mullen"
date: "September 21, 2015"
output: 
  html_document:
    keep_md: true
---

@@

```{r}
library("textreuse")

cache <- "cache/comparison-matrix-jaccard.rds"
if (!file.exists(cache)) {
  corpus <- readRDS("cache/corpus-skip-ngrams-n7k3.rds")
  m <- pairwise_compare(corpus, jaccard_similarity)
  saveRDS(m, cache)
} else {
  m <- readRDS(cache)
}
```

Here is the comparison matrix:

```{r}
m
```

>>>>

---
title: "Compare pairwise with Jaccard similarity"
author: "Lincoln Mullen"
date: "September 21, 2015"
---

```{r}
library("textreuse")
```

@@

We are going to test this with both shingled and skip n-grams. Here are skip n-grams.

```{r}
cache_skip <- "cache/comparison-matrix-skip-jaccard.rds"
if (!file.exists(cache_skip)) {
  corpus_skip <- readRDS("cache/corpus-skip-ngrams-n7k3.rds")
  m_skip <- pairwise_compare(corpus_skip, jaccard_similarity)
  saveRDS(m_skip, cache_skip)
} else {
  m_skip <- readRDS(cache_skip)
}
```

Here are shingled n-grams.

```{r}
cache_shingles <- "cache/comparison-matrix-shingles-jaccard.rds"
if (!file.exists(cache_shingles)) {
  corpus_shingles <- readRDS("cache/corpus-shingle-ngrams-n7.rds")
  m_shingles <- pairwise_compare(corpus_shingles, jaccard_similarity)
  saveRDS(m_shingles, cache_shingles)
} else {
  m_shingles <- readRDS(cache_shingles)
}
```

Here is the comparison matrix for the skip n-grams.

```{r}
round(m_skip, digits = 4)
```

Here is the comparison matrix for the shingled n-grams.

```{r}
round(m_shingles, digits = 4)
```

### 2015-10-08 016-manual-lsh.Rmd
Simplify notebook generation, improve figures

---
title: "Calculate minhash pairs manually"
author: "Lincoln Mullen"
date: "September 25, 2015"
output: 
  html_document:
    keep_md: true
---

@@

```{r message=FALSE}
library("textreuse")
library("dplyr")
library("digest")
library("stringr")
library("tidyr")
library("readr")
```

@@

```{r}
corpus <- readRDS("cache/corpus-n5-minhash-h1500-seed623.rds")
```

>>>>

---
title: "Calculate minhash pairs manually"
author: "Lincoln Mullen"
date: "September 25, 2015"
---

@@

```{r message=FALSE}
library("readr")
library("textreuse")
library("dplyr")
library("digest")
library("stringr")
library("tidyr")
```

@@

```{r}
cache <- "cache/corpus-n5-minhash-h1500-seed623.rds"
if (!file.exists(cache)) {
  corpus <- TextReuseCorpus(dir = "legal-codes-split", tokenizer = NULL)
  wc <- wordcount(corpus)
  corpus <- corpus[wc > 5]
  minhash <- minhash_generator(n = 1500, seed = 623)
  corpus <- tokenize(corpus, tokenizer = tokenize_ngrams, n = 5,
                     hash_func = minhash, keep_tokens = TRUE)
  saveRDS(corpus, file = cache)
} else {
  corpus <- readRDS(cache)
}
```
